The relative roles of genetic, ecological and environmental factors in species radiations

### 2017-09-22 paper/draft.tex
fix

Also: Ecological Opportunity and Adaptive Radiation, Stroud & Losos 2016: ``Does the concept have predictive value[...]?'' \cite{stroud2016ecological}
Phylogenetic niche conservatism, phylogenetic signal and the relationship between phylogenetic relatedness and ecological similarity among species, Losos 2008: ecological vs. phylogenetic similarity \cite{losos2008phylogenetic}

>>>>

Also: Ecological Opportunity and Adaptive Radiation, Stroud \& Losos 2016: ``Does the concept have predictive value[...]?'' \cite{stroud2016ecological}
Phylogenetic niche conservatism, phylogenetic signal and the relationship between phylogenetic relatedness and ecological similarity among species, Losos 2008: ecological vs. phylogenetic similarity \cite{losos2008phylogenetic}
